Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-05-27 fib2.tex
trivial changes.

\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
%\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4}
\usepackage{times}

@@

Below the (bond) percolation threshold for (say) a 2D square lattice, we expect random sets of 
bonds to decompose into separate clusters~\footnote{We use the word cluster to refer both to groupings of nearby anyons as formed by the decoding algorithm and to connected components of a graph under percolation, since both of these usages are standard in the literature. The intended meaning will remain clear from context.} of average size $O(\log(n))$ and variance 
$O(1)$~\cite{Bazant2000}.
Each noise process in our model is associated with a (randomly distributed) edge, and so 
disconnected clusters correspond to sets of anyons that could not have interacted at any 
point in their history. Although normally anyons can interact by braiding without ever coming into contact with one another, in this case charge conservation implies that each distinct cluster must have trivial total charge, and so all such interactions are trivial.
This allows us to simulate the braiding processes within each cluster 
separately. In other words: the quantum state in the fusion space of all anyons factorizes into 
a tensor product over bond clusters, and we can compute each factor separately. Since each 
cluster has size only $O(\log(n))$, we can typically simulate these dynamics efficiently 
because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. There are rare 
random processes that violate this reasoning, but processes such as these are suppressed 
exponentially in the lattice size $L$\cite{Grimmett1989}.

>>>>

\documentclass[aps, prl, letterpaper, twocolumn, superscriptaddress, notitlepage, 10pt]{revtex4-1}
\usepackage{times}

@@

Below the (bond) percolation threshold for (say) a 2D square lattice, we expect random sets of 
bonds to decompose into separate clusters~\footnote{We use the word cluster to refer both to groupings of nearby anyons as formed by the decoding algorithm and to connected components of a graph under percolation, since both of these usages are standard in the literature. The intended meaning will remain clear from context.} of average size $O(\log(n))$ and variance 
$O(1)$~\cite{Bazant2000}.
Each noise process in our model is associated with a (randomly distributed) edge, and so 
disconnected clusters correspond to sets of anyons that could not have interacted at any 
point in their history. Although normally anyons can interact by braiding without ever coming into contact with one another, in this case charge conservation implies that each distinct cluster must have trivial total charge, and so all such interactions are trivial.
This allows us to simulate the braiding processes within each cluster 
separately. In other words: the quantum state in the fusion space of all anyons factorizes into 
a tensor product over bond clusters, and we can compute each factor separately. Since each 
cluster has size only $O(\log(n))$, we can typically simulate these dynamics efficiently 
because the resulting fusion space has dimension $O(\mathrm{poly}(n))$. There are rare 
random processes that violate this reasoning, but processes such as these are suppressed 
exponentially in the lattice size $L$~\cite{Grimmett1989}.
